---
title: "Transomics 2.5D visualization Notebook"
output: html_notebook
---

# 1. Importing KEGG pathways with KEGGscape
```{r}
```


```{r}
library(RCy3)
```
- Installing KEGGscape App

```{r}
installApp('KEGGscape')
```

- Importing a kinase pathway

```{r}
library(httr)
GET("http://localhost:1234/keggscape/v1/mmu04150")
```

- Importing a substrate pathway

```{r}
GET("http://localhost:1234/keggscape/v1/mmu03008")
```

- Checking pathway networks in Cytoscape

```{r}
networks = getNetworkList()
```


# 2. Exporting, Replacing IDs, Combining pathways

## 2.1 Getting Node and Edge tables

- Setting current network to kinase layer, and getting node and edge tables

```{r}
setCurrentNetwork(networks[1]) # This works well from version 2.6.0 https://github.com/cytoscape/RCy3/issues/76
kinase_edge_table = getTableColumns('edge')
kinase_node_table = getTableColumns('node') # This works well from version 2.6.0 https://github.com/cytoscape/RCy3/issues/77
```

- Setting current network to substrate layer, and getting node and edge tables

```{r}
setCurrentNetwork(networks[2])
substrate_edge_table = getTableColumns('edge')
substrate_node_table = getTableColumns('node')
```

- Merging Networks




