---
title: "transomics2cytoscape"
author:
  - name: Kozo Nishida
    affiliation:
      - RIKEN Center for Biosystems Dynamics Research
    email: knishida@riken.jp
  - name: Katsuyuki Yugi
    affiliation:
      - RIKEN Center for Integrative Medical Sciences
    email: katsuyuki.yugi@riken.jp
date: "26 June 2020"
package: transomics2cytoscape
output:
    BiocStyle::html_document
vignette: |
    %\VignetteIndexEntry{transomics2cytoscape}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
    eval=FALSE
)
```

# Version Information
**R version**: R version 4.0.2 (2020-06-25)

**Bioconductor version**: 3.11

**Cytoscape**: 3.8.0

**Cy3D (Cytoscape app)**: 1.1.1

**KEGGscape (Cytoscape app)**: 0.8.2

# Introduction

To understand transomics datasets,
[Yugi et al.2014](https://pubmed.ncbi.nlm.nih.gov/25131207)
has proposed a method for network visualization
by integrating multiple pathways in 3D space.

The 3D network visualization was created by
[VANTED](https://pubmed.ncbi.nlm.nih.gov/23140568)
and manual operation. transomics2cytoscape automatically
creates the network data for Cytoscape and
[Cy3D](http://apps.cytoscape.org/apps/cy3d) renderer
using
[Cytoscape Automation](https://pubmed.ncbi.nlm.nih.gov/31477170).

## Installation

```{R}
# devtools::install_github("ecell/transomics2cytoscape", build_vignettes = TRUE)
```

# Package Content

## Sample data

## 3D network visualization for transomics

```{r setup}
# suppressPackageStartupMessages(library(dplyr))
# suppressPackageStartupMessages(library(RCy3))
# suppressPackageStartupMessages(library(KEGGREST))
# Sys.setenv(LANGUAGE="en_US.UTF-8") 
library(dplyr)
library(RCy3)
library(KEGGREST)
library(transomics2cytoscape)
kinase2enzyme <- system.file("extdata", "kinase_enzyme.txt",
    package = "transomics2cytoscape")
stylexml <- system.file("extdata", "transomics.xml",
    package = "transomics2cytoscape")
create3Dnetwork(c(rno00010=1, rno00010=200, rno04910=400, rno04910=600),
    kinase2enzyme, stylexml)
```

# Workflow steps

## Session information {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```