---
title: "transomics2cytoscape"
author: "Kozo Nishida"
date: "2/26/2020"
package: transomics2cytoscape
output:
    BiocStyle::html_document
vignette: |
    %\VignetteIndexEntry{transomics2cytoscape}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::rmarkdown}
---

## Introduction

To understand transomics datasets, [Yugi et al.
2014](https://pubmed.ncbi.nlm.nih.gov/25131207)
has proposed a method for network visualization
by integrating multiple pathways in 3D space.

The 3D network visualization was created by
[VANTED](https://pubmed.ncbi.nlm.nih.gov/23140568)
and manual operation. transomics2cytoscape automatically
creates the network data for Cytoscape and
[Cy3D](http://apps.cytoscape.org/apps/cy3d) renderer
using
[Cytoscape Automation](https://pubmed.ncbi.nlm.nih.gov/31477170).

## Installation

```{R}
# devtools::install_github("ecell/transomics2cytoscape", build_vignettes = TRUE)
```

## Usage

```{r setup}
# suppressPackageStartupMessages(library(dplyr))
# suppressPackageStartupMessages(library(RCy3))
# suppressPackageStartupMessages(library(KEGGREST))
# Sys.setenv(LANGUAGE="en_US.UTF-8") 
library(dplyr)
library(RCy3)
library(KEGGREST)
library(transomics2cytoscape)
kinase2enzyme <- system.file("extdata", "kinase_enzyme.txt",
                             package = "transomics2cytoscape")
print(kinase2enzyme)
create3Dcyjs("rno00010", "rno00010", "rno04910", 1, 200, 400,
             kinase2enzyme, "transomics3D.cyjs")
```

## 3D visualization with Cy3D

Since Cytoscape Automation cannot select Cy3D network renderer,
You need to import the output.cyjs using the Cytoscape GUI.

Now you should see the following 3D visualization:


## Session information {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```